### 2015-11-04 CVPR16/Source/experiments.tex
Updated RAS results with sequence 4 results.

\begin{figure*}
\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
  \caption{Association errors on different sets of point tracks. The
    numbers on y-axis represent the data sequence number in KITTI dataset. The
    first set of bars in each plot correspond to the mean across all sequences.
    The error is in terms of average fraction of foreground points incorrectly
    associated to objects per sequence.}
\label{fig:assoc-occ-results}
\end{figure*}
\begin{table}
\begin{tabular}{lrrrr}
  \toprule
  & Ours & BBox & BM & RAS\\
  \midrule
  Dyn. and occ. tracks        & \textbf{13.2} & 21.3 & 30.9 & 29.3 \\
  Occluded tracks             & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
  Dynamic tracks              & \textbf{06.6} & 11.4 & 15.3 & 16.4 \\
  All tracks                  & \textbf{08.6} & 12.6 & 21.9 & 21.5 \\
  \bottomrule
\end{tabular}
\caption{Mean association experiment results in error percentage calculated as percentage of points wrongly associated.}
\label{tab:meanAssoc}
\end{table}

>>>>

\begin{figure*}
\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
  \caption{Association errors on different sets of point tracks. The
    numbers on y-axis represent the data sequence number in KITTI dataset. The
    first set of bars in each plot correspond to the mean across all sequences.
    The error is in terms of average fraction of foreground points incorrectly
    associated to objects per sequence.}
\label{fig:assoc-occ-results}
\end{figure*}
\begin{table}
\begin{tabular}{lrrrr}
  \toprule
  & Ours & BBox & BM & RAS\\
  \midrule
  Dyn. and occ. tracks        & \textbf{13.2} & 21.3 & 30.9 & 30.1 \\
  Occluded tracks             & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
  Dynamic tracks              & \textbf{06.6} & 11.4 & 15.3 & 17.7 \\
  All tracks                  & \textbf{08.6} & 12.6 & 21.9 & 21.5 \\
  \bottomrule
\end{tabular}
\caption{Mean association experiment results in error percentage calculated as percentage of points wrongly associated.}
\label{tab:meanAssoc}
\end{table}
